```{r libraries}
if (!require(skimr)) install.packages('skimr')
if (!require(lubridate)) install.packages('lubridate')
if (!require(tidyverse)) install.packages('tidyverse')
if (!requireNamespace("devtools")) {
  install.packages("devtools")
}
if (!require(easystats)) devtools::install_github("easystats/easystats")
```
```{r lib2}
if (!require(ggthemes)) install.packages('ggthemes')
if (!require(pmdplyr)) install.packages("pmdplyr")
if (!require(kableExtra)) install.packages("kableExtra")
```

## Import Data

```{r data1}
nz_0 <- 
  readr::read_csv2(
    url("https://raw.githubusercontent.com/go-bayes/psych-447/main/data/nz/nz.csv")
    )
```

```{r data2}
f<-c("None Of The Time",
     "A Little Of The Time",
     "Some Of The Time",
     "Most Of The Time",
     "All Of The Time")
```

```{r tidy}
if (!require(tidyverse)) install.packages('tidyverse')
```

```{r data3}
nz <- nz_0 %>%
  dplyr::mutate_if(is.character, factor) %>%
  select(
    -c(
      SWB.Kessler01,
      SWB.Kessler02,
      SWB.Kessler03,
      SWB.Kessler04,
      SWB.Kessler05,
      SWB.Kessler06
    )
  ) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  mutate(FeelHopeless = forcats::fct_relevel(FeelHopeless, f)) %>%
  mutate(FeelDepressed = forcats::fct_relevel(FeelDepressed, f)) %>%
  mutate(FeelRestless = forcats::fct_relevel(FeelRestless, f)) %>%
  mutate(EverythingIsEffort = forcats::fct_relevel(EverythingIsEffort, f)) %>%
  mutate(FeelWorthless = forcats::fct_relevel(FeelWorthless, f)) %>%
  mutate(FeelNervous = forcats::fct_relevel(FeelNervous, f)) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(date = make_date(year = 2009, month = 6, day = 30) + TSCORE)
```

Question 1
## Integer

```{r camtaylor}
nz %>%
  select(contains("hour"))
```
```{r integer1}
nz2 <- nz %>%
dplyr::mutate(as.integer(HLTH.SleepHours)) %>%
dplyr::mutate(as.integer(Hours.Internet)) %>%
dplyr::mutate(as.integer(Hours.Exercise)) %>%
dplyr::mutate(as.integer(Hours.Work)) %>%
dplyr::mutate(as.integer(Hours.News)) %>%
dplyr::mutate(as.integer(HoursCharity))
```

Question 2a
## Scale, Center, Transform

```{r imsadrn}
nz3 <- nz2 %>%
  select(Pol.Orient)%>%
  mutate(Pol.Orient = scale(Pol.Orient, scale = TRUE, center  = TRUE))
head(nz3)
```

Create a new indicator that standardises the Pol.Orient variable, create a new indicator that centers the Pol.Orient variable, create a new indicator that centres the Age variable in decade-long units. Do this in a single piped workflow.

Question 2b
## Scale, Center, Transform

Question 3
## Scale, Center, Transform

Question 4
## Scale, Center, Transform

Question 5
## Scale, Center, Transform

Question 6
## Scale, Center, Transform

Question 7
## Scale, Center, Transform

Question 8
## Scale, Center, Transform

Question 9
## Scale, Center, Transform

Question 10
## Scale, Center, Transform
