---
output:
  word_document: default
  html_document: default
  always_allow_html: true
---
```{r libraries}
if (!require(skimr)) install.packages('skimr')
if (!require(lubridate)) install.packages('lubridate')
if (!require(tidyverse)) install.packages('tidyverse')
if (!requireNamespace("devtools")) {
  install.packages("devtools")
}
if (!require(easystats)) devtools::install_github("easystats/easystats")
```
```{r lib2}
if (!require(ggthemes)) install.packages('ggthemes')
if (!require(pmdplyr)) install.packages("pmdplyr")
if (!require(kableExtra)) install.packages("kableExtra")
```

## Import Data

```{r data1}
nz_0 <- 
  readr::read_csv2(
    url("https://raw.githubusercontent.com/go-bayes/psych-447/main/data/nz/nz.csv")
    )
```

```{r data2}
f<-c("None Of The Time",
     "A Little Of The Time",
     "Some Of The Time",
     "Most Of The Time",
     "All Of The Time")
```

```{r tidy}
if (!require(tidyverse)) install.packages('tidyverse')
```

```{r data3}
nz <- nz_0 %>%
  dplyr::mutate_if(is.character, factor) %>%
  select(
    -c(
      SWB.Kessler01,
      SWB.Kessler02,
      SWB.Kessler03,
      SWB.Kessler04,
      SWB.Kessler05,
      SWB.Kessler06
    )
  ) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  mutate(FeelHopeless = forcats::fct_relevel(FeelHopeless, f)) %>%
  mutate(FeelDepressed = forcats::fct_relevel(FeelDepressed, f)) %>%
  mutate(FeelRestless = forcats::fct_relevel(FeelRestless, f)) %>%
  mutate(EverythingIsEffort = forcats::fct_relevel(EverythingIsEffort, f)) %>%
  mutate(FeelWorthless = forcats::fct_relevel(FeelWorthless, f)) %>%
  mutate(FeelNervous = forcats::fct_relevel(FeelNervous, f)) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(date = make_date(year = 2009, month = 6, day = 30) + TSCORE)
```

Question 1
## Integer

```{r camtaylor}
nz %>%
  select(contains("hour"))
```
```{r integer22}
nz2 <- nz %>%
  mutate(Hours.Internet_int = as.integer(Hours.Internet),
  Hours.Exercise_int = as.integer(Hours.Exercise),
  Hours.Work_int = as.integer(Hours.Work),
  Hours.News_int = as.integer(Hours.News),
  HoursCharity_int = as.integer(HoursCharity))
```

```{r STD}
str(nz2)
```

Question 2a
## Scale, Center, Transform

```{r imsadrn}
nz3 <- nz2 %>%
  select(Pol.Orient, Age)%>%
  mutate(Pol.Orient1 = scale(Pol.Orient, scale = TRUE, center  = TRUE)) %>%
  mutate(Pol.Orient2 = scale(Pol.Orient, scale = FALSE, center = TRUE)) %>%
  mutate(Age1 = scale(Age, scale = FALSE, center  = TRUE)/10)
head(nz3)
```
Question 2b
## Data Wrangle

```{r wrangle}
nz4 <- nz %>%
  select(Hours.Exercise, Wave) %>%
  mutate(Hours.Exercise44 = scale(Hours.Exercise, scale = TRUE, center  = TRUE)) %>%
  filter(Wave !="2019")

## Compare

summary(nz4$Hours.Exercise44)
summary(nz4$Wave)

nz4
```

Question 3
## Working with dates

```{r wannagoonadate}
datrep <- nz %>%
  count(day = floor_date(date, "day"))%>%
  dplyr::mutate(Year = factor(ifelse(
    day < "2018-01-01",
    2017,
    ifelse(day < "2019-01-01", 2018,
           ifelse(day < "2020-01-01", 2019, 2020))
  ))) %>%
  arrange(day)
```

```{r d8m8}
datrep%>%
  arrange(desc(n))
```

Maxmimum for 2019: 54
Maximum for 2018: 112 based from the above summary and pulling the relevant dates out from it.

Question 4
## Calculating dates and creating summaries

How many days are there between the date with the highest number of responses and the date with the second highest number of responses? Pulling the relevant data from the above summary: the answer is 1 day between these dates. 

*Bonus*: Calculate difference between the number of responses on the highest response date and second highest response date? See below:

```{r BONUSyall}
112-93
```

Question 5
## Working with date intervals

```{r jordanandparis}
int<-lubridate::interval(ymd_hms("1995-12-25-05-02-22"), ymd_hms("2021-03-20-13-22-04"))
time_length(int, "month")
```

Question 6
## Create an ordered factor from numerical data

```{r factor3452}
nz7 <-nz %>%
  dplyr::mutate(relichurchy = cut(
    Religion.Church,
    breaks = c(-Inf, 0, 4, Inf),  
    labels = c("Non-attendance", "Moderate attendance", "Frequent attendance"), 
    right = TRUE
  ))
table(nz7$relichurchy, useNA = "ifany")
```

*Make sure to re-level the factor so that the ordinal ranking moves from lowest to highest: because the factors are already leveled correctly, no re-leveling is required - 
re-leveling could otherwise be done with the re-level function

Question 7a
## Make a summary table

```{r liahelper}
nz5 <- nz %>%
  select(date, HLTH.SleepHours) %>%
  mutate(Months = month(date, label = TRUE)) %>%
  group_by(Months) %>%
  arrange(Months)
```

```{r kablekable}
library(kableExtra)
nz5 %>%
  select(HLTH.SleepHours, Months) %>%
  filter(!is.na(HLTH.SleepHours))%>%
  group_by(Months) %>%
  summarise(av_sleep = mean(HLTH.SleepHours, na.rm = T))%>%
  pivot_wider(names_from = Months, values_from = av_sleep) %>%
  kbl(caption = "Average Number of Hours of Sleep by Month") %>%
   kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%
  collapse_rows()
```

Question 7b
## Make a summary graph

```{r Parissavinglives}
sleep <- nz %>%
  select(date, HLTH.SleepHours) %>%
  mutate(Months = month(date, label = TRUE)) %>%
  group_by(Months) %>%
  summarise(
    mn_sleep =  mean(HLTH.SleepHours, na.rm = TRUE),
    sd_sleep =  sd(HLTH.SleepHours, na.rm = TRUE),
    n_sleep = n()
  ) %>%
  mutate(
    se_sleep = sd_sleep / sqrt(n_sleep),
    lw_ci = mn_sleep - qt(1 - (0.05 / 2), n_sleep - 1) * se_sleep,
    up_ci = mn_sleep + qt(1 - (0.05 / 2), n_sleep - 1) * se_sleep
  ) %>%
  ggplot(., aes(x = Months, y = mn_sleep, colour = mn_sleep)) +
  geom_errorbar(aes(ymin = lw_ci, ymax = up_ci), width = .1) +
  geom_point(size = 3)  +
  scale_y_continuous(limits = c(1,8)) + 
  theme_classic() + scale_fill_viridis_d()
sleep
```
Briefly explain why some intervals are wider than others.

typically, my understanding is that wider CI's imply less certainty about what the true population mean is. Given we are 95% sure the mean is within those intervals, if it's wider, that means we are less sure of what it is because we need to widen to intervals to capture that 95% certainty of our estimate of the mean. Those wider intervals (occuring in autumn and spring) have that less certainty of the estimatation of the mean sleep amount in those months, and my initial thought was because of daylights saving happening around those months, yet if that were true, where daylights saving ends (April) should have less sleep than when it starts (Septempber), but is the other way around which is surprising , and so that inference seems to be blown out the water. 

Question 8
## Correlation graph

```{r corrgraph}
nz8 <- nz %>%
  mutate(FeelHopeless_int = as.integer(FeelHopeless),
  FeelDepressed_int = as.integer(FeelDepressed),
  FeelRestless_int = as.integer(FeelRestless),
  EverythingIsEffort_int = as.integer(EverythingIsEffort),
  FeelWorthless_int = as.integer(FeelWorthless),
  FeelNervous_int = as.integer(FeelNervous))
```

```{r corrgraph2}
moodnz <- nz%>%
  select(
    FeelHopeless,
    FeelDepressed,
    FeelRestless,
    EverythingIsEffort,
    FeelWorthless,
    FeelNervous,
    KESSLER6sum
  ) %>%
  mutate_all(., as.numeric) %>% #make numeric 
  mutate(KESSLER6sum = as.factor(KESSLER6sum),
         FeelNervous = log(FeelNervous + 1))
```

```{r correr23r5}
library(correlation)
library(ggraph)
p1<-moodnz %>%
  correlation(partial = FALSE, multilevel = TRUE ) %>%
  plot()
```

```{r corrfinal}
moodnz %>%
  correlation(partial = FALSE, multilevel = TRUE ) %>%
  summary()
```
```{r anothercorr}
library(correlation)
p2<-moodnz %>%
  select(-KESSLER6sum)%>% # get rid of grouping variable
  correlation(partial = FALSE, multilevel = FALSE ) %>%
  plot()
```

```{r anotherone}
moodnz %>%
  select(-KESSLER6sum)%>% # get rid of grouping variable
  correlation(partial = FALSE, multilevel = FALSE ) %>%
  summary()
```
```{r plotplot}
library(patchwork)
# create a two panel plot
p1 / p2 + 
  plot_annotation(title = "Plot of multilevel (a) and single-level (b) correlation", tag_levels = 'a')
```

*What do you find most interesting about this plot?* The strong correlations present between feeling worthless, depressed, and hopeless. However, I can't see the strength of the "FeelWorthless" to "FeelDepressed" correlation nor waht exactly is going on with the negative R scores in plot (A). 

Question 9
## Create a blank papaja report

See attached. 

Question 10
## Patchwork

Use the patchwork library to create a figure with two plots on top of each other. Use the tag_levels function to index each of the two plots. The graphs should describe some dimension of the truncated nz dataset.

```{r patchwork}
p3 <- ggplot(data = nz, aes(x = KESSLER6sum, y = FeelDepressed, fill = FeelDepressed)) +
  geom_boxplot(notch = FALSE) + scale_fill_viridis_d()+
  ggtitle('People Who Are Feeling Depressed')

p4 <- ggplot (data = nz, aes(x = KESSLER6sum, y = FeelNervous, fill = FeelNervous)) +
  geom_boxplot(notch = FALSE) + scale_fill_viridis_d()+
  ggtitle('People Who Are Feeling Nervous')

p3/
  p4
```